---
title: "LAB10"
output: 
    github_document:
    html_preview: false
    html_document:
    df_print: paged
    always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(repos = c(CRAN = "http://cran.rstudio.com"))
```

```{r}
library(RSQLite)
library(DBI)
```

```{r}
# Initialize a temporary in memory database
con <- dbConnect(SQLite(), ":memory:")

# Download tables
actor <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/actor.csv")
rental <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/rental.csv")
customer <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/customer.csv")
payment <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/payment_p2007_01.csv")

# Copy data.frames to database
dbWriteTable(con, "actor", actor)
dbWriteTable(con, "rental", rental)
dbWriteTable(con, "customer", customer)
dbWriteTable(con, "payment", payment)
```

```{r}
dbListTables(con)
```

### Exercise 1:Retrive the actor ID, first name and last name for all actors using the actor table. Sort by last name and then by first name.
```{r}
ex1<- dbGetQuery(con,
      "SELECT actor_id, last_name, first_name
      FROM actor
      ORDER by last_name, first_name
      LIMIT 5  /*report first 5 records */")
ex1
```
### Exercise 2: Retrive the actor ID, first name, and last name for actors whose last name equals ‘WILLIAMS’ or ‘DAVIS’.
```{r}
ex2<- dbGetQuery(con,
      "SELECT actor_id, last_name, first_name
      FROM actor
      WHERE last_name IN ('WILLIAMS', 'DAVIS') 
      LIMIT 5  /*report first 5 records */")
ex2
```
### Exercise 3:Write a query against the rental table that returns the IDs of the customers who rented a film on July 5, 2005 (use the rental.rental_date column, and you can use the date() function to ignore the time component). Include a single row for each distinct customer ID.
```{r}
ex3<- dbGetQuery(con,
      "SELECT DISTINCT customer_id
      FROM rental
      WHERE date(rental_date) = '2005-07-05'
      LIMIT 5")
ex3
```
### Exercise 4.1: Construct a query that retrives all rows from the payment table where the amount is either 1.99, 7.99, 9.99.

```{r}
ex4_1<-dbSendQuery(con,"
SELECT *
FROM payment
WHERE amount IN (1.99, 7.99, 9.99)")

dbFetch(ex4_1, n=10)
```
### Exercise 4.2:Construct a query that retrives all rows from the payment table where the amount is greater then 5.
```{r}
ex4_2<-dbGetQuery(con,"
SELECT *
FROM payment
WHERE amount > 5
LIMIT 5"
)
ex4_2
```
### Exercise 4.3:Construct a query that retrives all rows from the payment table where the amount is greater then 5 and less then 8
```{r}
ex4_3<-dbGetQuery(con,"
SELECT *
FROM payment
WHERE amount > 5 and amount < 8
LIMIT 5"
)
ex4_3
```
Bonus: Count how many are?
```{r}
Bonus<-dbGetQuery(con,"
SELECT COUNT(*)
FROM payment
WHERE amount > 5
LIMIT 5"
)
Bonus
```
Counting per staff 'staff_id'
```{r}
staff<-dbGetQuery(con,"
SELECT staff_id, COUNT (*) AS N
FROM payment
WHERE amount > 5
GROUP BY staff_id
")
staff
```

### Exercise 5: Retrive all the payment IDs and their amount from the customers whose last name is ‘DAVIS’.
```{r}
ex5<-dbGetQuery(con,"
SELECT p.payment_id, p.amount
FROM payment AS p
  INNER JOIN customer AS c ON p.customer_id=c.customer_id
where c.last_name = 'DAVIS'"
)
ex5
```
### Exercise 6.1:Use COUNT(*) to count the number of rows in rental
```{r}
ex6_1<-dbGetQuery(con,"
SELECT COUNT (*)
FROM rental
")
ex6_1
```

### Exercise 6.2:Use COUNT(*) and GROUP BY to count the number of rentals for each customer_id
```{r}
ex6_2<-dbGetQuery(con,"
SELECT customer_id, COUNT (*) AS 'N Rentals'
FROM rental
GROUP BY customer_id
LIMIT 10
")
ex6_2
```
### Exercise 6.3:Repeat the previous query and sort by the count in descending order
```{r}
ex6_3<-dbGetQuery(con,"
SELECT customer_id, COUNT (*) AS 'N Rentals' 
FROM rental
GROUP BY customer_id
ORDER BY COUNT (*) DESC 
LIMIT 10
")
ex6_3
```
### Exercise 6.4 :Repeat the previous query but use HAVING to only keep the groups with 40 or more.
```{r}
ex6_4<-dbGetQuery(con,"
SELECT customer_id, COUNT (*) AS 'N Rentals' 
FROM rental
GROUP BY customer_id
HAVING COUNT(*) >= 40
ORDER BY COUNT (*) DESC 
LIMIT 10
")
ex6_4
```
### Exercise 7:The following query calculates a number of summary statistics for the payment table using MAX, MIN, AVG and SUM
```{r}
ex7<-dbGetQuery(con,"
SELECT MAX(amount) AS max_amount, MIN(amount) AS min_amount, AVG(amount) AS avg_amount, SUM(amount) AS sum_amount
FROM payment
")
ex7
```
### Exercise 7.1:Modify the above query to do those calculations for each customer_id
```{r}
ex7_1<-dbGetQuery(con,"
SELECT customer_id, MAX(amount) AS max_amount, MIN(amount) AS min_amount, AVG(amount) AS avg_amount, SUM(amount) AS sum_amount
FROM payment
GROUP BY customer_id 
LIMIT 10
")
ex7_1
```

### Exercise 7.2:Modify the above query to only keep the customer_ids that have more then 5 payments
```{r}
ex7_2<-dbGetQuery(con,"
SELECT customer_id, COUNT(*) AS N, MAX(amount) AS max_amount, MIN(amount) AS min_amount, AVG(amount) AS avg_amount, SUM(amount) AS sum_amount
FROM payment
GROUP BY customer_id 
HAVING COUNT(*) >5
LIMIT 10
")
ex7_2

```



### Clean Up:
```{r}
dbDisconnect(con)
```







