---
title: "LAB10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(repos = c(CRAN = "http://cran.rstudio.com"))
```

```{r}
library(RSQLite)
library(DBI)
```

```{r}
# Initialize a temporary in memory database
con <- dbConnect(SQLite(), ":memory:")

# Download tables
actor <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/actor.csv")
rental <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/rental.csv")
customer <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/customer.csv")
payment <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/payment_p2007_01.csv")

# Copy data.frames to database
dbWriteTable(con, "actor", actor)
dbWriteTable(con, "rental", rental)
dbWriteTable(con, "customer", customer)
dbWriteTable(con, "payment", payment)
```

```{r}
dbListTables(con)
```

### Exercise 1:Retrive the actor ID, first name and last name for all actors using the actor table. Sort by last name and then by first name.
```{r}
ex1<- dbGetQuery(con,
      "SELECT actor_id, last_name, first_name
      FROM actor
      ORDER by last_name, first_name
      LIMIT 5  /*report first 5 records */")
ex1
```
### Exercise 2: Retrive the actor ID, first name, and last name for actors whose last name equals ‘WILLIAMS’ or ‘DAVIS’.
```{r}
ex2<- dbGetQuery(con,
      "SELECT actor_id, last_name, first_name
      FROM actor
      WHERE last_name IN ('WILLIAMS', 'DAVIS') 
      LIMIT 5  /*report first 5 records */")
ex2
```
### Exercise 3:Write a query against the rental table that returns the IDs of the customers who rented a film on July 5, 2005 (use the rental.rental_date column, and you can use the date() function to ignore the time component). Include a single row for each distinct customer ID.
```{r}
ex3<- dbGetQuery(con,
      "SELECT DISTINCT customer_id
      FROM rental
      WHERE date(return_date) = '2005-07-05'
      LIMIT 5")
ex3
```
### Exercise 4.1: Construct a query that retrives all rows from the payment table where the amount is either 1.99, 7.99, 9.99.

```{r}
ex4_1<-dbSendQuery(con,"
SELECT *
FROM payment
WHERE amount IN (1.99, 7.99, 9.99)")

dbFetch(ex4_1, n=10)
```
### Exercise 4.2:Construct a query that retrives all rows from the payment table where the amount is greater then 5.
```{r}
ex4_2<-dbGetQuery(con,"
SELECT *
FROM payment
WHERE amount > 5
LIMIT 5"
)
ex4_2
```
### Exercise 4.3:Construct a query that retrives all rows from the payment table where the amount is greater then 5 and less then 8
```{r}
ex4_3<-dbGetQuery(con,"
SELECT *
FROM payment
WHERE amount > 5 and amount < 8
LIMIT 5"
)
ex4_3
```
Bonus: Count how many are?
```{r}
Bonus<-dbGetQuery(con,"
SELECT COUNT(*)
FROM payment
WHERE amount > 5
LIMIT 5"
)
Bonus
```
Counting per staff 'staff_id'
```{r}
staff<-dbGetQuery(con,"
SELECT staff_id COUNT (*) AS N
FROM payment
WHERE amount > 5
GROUP BY staff_id
")
staff
```

### Exercise 5: Retrive all the payment IDs and their amount from the customers whose last name is ‘DAVIS’.
```{r}

```
















