---
title: "LAB6"
output: 
    github_document:
    html_preview: false
    html_document:
    df_print: paged
    always_allow_html: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(tibble)
library(tidytext)
library(ggplot2)
```


```{r get data}
fn<-"mtsamples.csv"
if (!file.exists(fn))
  download.file("https://raw.githubusercontent.com/USCbiostats/data-science-data/master/00_mtsamples/mtsamples.csv",
    destfile = fn
    )

mtsamples<-read.csv(fn)
mtsamples<-as.tibble(mtsamples)
head(mtsamples)

```
## Question 1: How many and how are specialties
```{r}
specialties<-mtsamples %>%
  count(medical_specialty)

specialties %>%
  arrange(desc(n))%>%
  top_n(15)%>%
  knitr::kable()
```

```{r dist}
# Method 1: Not that pretty
ggplot(mtsamples, aes(x=medical_specialty))+
      geom_histogram(stat="count")+
      coord_flip()

# Method 2:
ggplot(specialties, aes(x=n, y=fct_reorder(medical_specialty,n)))+
  geom_col()
         
```
# Question 2:
```{r token-transcript, cache=TRUE}
mtsamples %>%
  unnest_tokens(output=word, input=transcription) %>%
  count(word, sort = TRUE) %>%
  top_n(20) %>%
  ggplot(aes(x=n, y=fct_reorder(word, n))) +
  geom_col()
```
## Note that "patient" seems important.

# Question 3:
```{r}
mtsamples %>%
  unnest_tokens(output=word, input=transcription) %>%
  count(word, sort = TRUE) %>%  
  anti_join(stop_words, by="word")%>%
  # Using regular expression to remove numbers
  filter(!grepl("^[0-9]+$", x= word))%>%
  top_n(20) %>%
  ggplot(aes(x=n, y=fct_reorder(word, n))) +
  geom_col()

# Looking better, but we don't like numbers.
```
# Question 4: Repeat question 2, but this time tokenize into bi-grams. how does the result change if you look at tri-grams?
```{r}
# Bigram
mtsamples %>%
  unnest_ngrams(output=bigram, input=transcription,n=2) %>%
  count(bigram, sort = TRUE) %>%
  top_n(20) %>%
  ggplot(aes(x=n, y=fct_reorder(bigram, n))) +
  geom_col()

#Trigram
mtsamples %>%
  unnest_ngrams(output=trigram, input=transcription,n=3) %>%
  count(trigram, sort = TRUE) %>%
  top_n(20) %>%
  ggplot(aes(x=n, y=fct_reorder(trigram, n))) +
  geom_col()
```
Now some phrases start to show up like "tolerated the procedure"

# Question 5:
```{r warning=FALSE}
bigrams <-mtsamples %>%
  unnest_ngrams(output=bigram, input=transcription,n=2) %>%
  separate(bigram,into =c("w1","w2"),sep=" ")
  
bigrams %>% 
  filter(w1=="there")%>%
  select(w1,w2)%>%
  count(w2, sort =TRUE)

bigrams %>% 
  filter(w2=="is")%>%
  select(w1,w2)%>%
  count(w1, sort =TRUE)
```
since we are looking at single word again, it's a good idea to treat these as single tokens. So let's remove the stop-word and the numbers

```{r there-word-stop}
# Words after "there" without stop word and numbers
bigrams %>% 
  filter(w1=="there") %>%
  filter(!(w2 %in% stop_words$word)&!grepl("^[0-9]+$",w2)) %>%
  count(w2,sort=TRUE)%>%
  top_n(10)%>%
  knitr::kable()

# Words before "is" without stop word or numbers
bigrams %>% 
  filter(w2=="is") %>%
  filter(!(w1 %in% stop_words$word)&!grepl("^[0-9]+$",w1)) %>%
  count(w1,sort=TRUE)%>%
  top_n(10)%>%
  knitr::kable()
```

# Question 6: Which words are most used in each of the specialties. you can use group_by() and top_n() from dplyr to have the calculations be done within each specialty. Remember to remove stopwords. How about the most 5 used words?
```{r}
mtsamples %>% 
  unnest_tokens(word, input=transcription)%>%
  group_by(medical_specialty)%>%
  count(word,sort=TRUE)%>%
  filter(!(word %in% stop_words$word)&!grepl("^[0-9]+$",word)) %>%
  top_n(5)%>%
  arrange(medical_specialty,desc(n))%>%
  knitr::kable()
  

```


